Explicit Operations on Parametrised Polytopes

### 2018-01-07 dcg-draft.tex
Highlighted revision of Corollary 2

The polytopic parametric set-valued map $\mathcal W(p):=\{z: a_i z + b_i p\leq c_i \; \forall i\in\mathbb N_m\}$
is not parametrically convex for any $B^T = [\begin{matrix} b_1^T & \cdots & b_m^T\end{matrix}]$ with $\text{rank}(B)>1$.

@@

First, assume $\text{rank}(B)=0$, in this case the graph $\mathscr G(\mathcal W)$ is constant for all $p$

@@

For $\text{rank}(B)>2$ the graph $\mathscr G(\mathcal W)$ is given by a convex polyhedron with vertices in the parameter space, which implies that the graph is locally strictly convex and $\mathcal W(p)$ therefore violates Theorem~\ref{thm:p:convexity:graph}.

>>>>

\revision{The polytopic parametric set-valued map $\mathcal W(p):=\{z: a_i z + b_i p\leq c_i \; \forall i\in\mathbb N_m\}$
is not parametrically convex for any $B^T = [\begin{matrix} b_1^T & \cdots & b_m^T\end{matrix}]$ with $\text{rank}(B)>1$.}

@@

\revision{First, assume $\text{rank}(B)=0$, in this case the graph $\mathscr G(\mathcal W)$ is constant for all $p$

@@

For $\text{rank}(B)>2$ the graph $\mathscr G(\mathcal W)$ is given by a convex polyhedron with vertices in the parameter space, which implies that the graph is locally strictly convex and $\mathcal W(p)$ therefore violates Theorem~\ref{thm:p:convexity:graph}.}
